Introduction

### 2015-07-21 dissertation/problems.tex
The MOP for dynamic programming

>>>>

I believe that the core of Problem~\ref{prob:dynaprog} lies in the
prevalence of statically typed languages. From an engineering
perspective, static typing seems like a good idea, since errors should
surface at compile time. However, it seems like it comes at a high
cost: Programmers seem incapable of thinking beyond the constraints it
sets. Nevertheless, the theoretical framework that seems to solve the
problem was proposed in 1991 in the book ``The art of the metaobject
protocol'' \cite{kiczales1991art}. Perl has a mature implementation of
the metaobject protocol, and the topic has been discussed on several
hackathons, and some code has been written, but the solution seems
elusive.
